Smart Drill-Down

### 2015-04-07 TableSummarization/Paper/KDDrebuttal.tex

\documentclass{article}
\date{\today}

\begin{document}

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle
To the editors,

We would like to thank the reviewers for their insightful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in the pattern mining area. We went through several of the papers pointed out by the reviewers, and will mention the differences between these papers and our work below. We will also do a more thorough literature review and significantly augment the related work section for the camera ready submission.

There are four primary ways in which existing work on pattern mining differs from our work:
\begin{enumerate}
\item {\bf Interactiveness}: user guided. fast (making approximation necessary).

\item {\bf Relational Data}: gives meaning to interestingness measures based on columns, such as `Bits'.

\item {\bf Tunability}: The primary attribute of our work is that we allow the user to specify the kind of rules/patterns he is interested in by providing any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an approximate optimality guarantee. This is in contrast to several of the related papers, where the authors use a heuristic algorithm such as beam search, or a restricted top down search, with no theoretical optimality guarantees. 
% mention paper names/authors above

\item {\bf Theoretical Guarantees}:
\end{enumerate}

% address other reviewer comments, especially 4th reviewers.

\end{document}

### 2015-04-09 TableSummarization/Paper/KDDrebuttal.tex

\begin{document}

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle
To the editors,

We would like to thank the reviewers for their insightful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in the pattern mining area. We went through several of the papers pointed out by the reviewers, and will mention the differences between these papers and our work below. We will also do a more thorough literature review and significantly augment the related work section for the camera ready submission.

There are three primary ways in which existing work on pattern mining differs from our work:
\begin{enumerate}
\item {\bf Interactiveness}: Smart drill-down allows the user to direct the data exploration according to his interests. This means that in each step, the number of rules displayed to the user should be small enough to be readable in a short amount of time, and the next set of rules to be displayed should depend on what part of the table the user expresses interest in. In addition, the response time of the system needs to be small ($< 10$ seconds) in order to prevent the user's flow of thought from being broken. In contrast, many of the mentioned related works (e.g. `The Chosen few', `Constraint based Pattern Mining') display {\em all} output patterns in one go, which would take a lot of processing time and potentially display unneeded information to the user. Some, such as `Krimp', `Summarizing Itemset Patterns: A Profile-Based Approach' display a smaller number of patterns, but are still not interactive.

\item {\bf Relational Data}: Smart drill-down is used for summarizing data from a relational table, as opposed to a set of transactions. Different columns in a table can be of differing importance to a user, and smart drill-down allows a user to focus on expanding certain columns, or to ignore certain columns. In a transaction based database, it is much harder to express extra interest in certain `types' of items.

\item {\bf Tunability}: An important attribute of our work is that we allow the user to specify the kind of rules he is interested in by specifying any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an {\em approximate optimality guarantee}. Thus we attempt to strike a fine balance between tunability and optimizability. This is in contrast to several of the related papers with a fully general scoring function (`Diverse subgroup set discovery', ), forcing the authors use an algorithm that is either heuristic with no optimality guarantees, or very time consuming. Some other papers (`MIME', `One click mining') are not tunable enough, and only provide a fixed set of interestingess parameters. 
\end{enumerate}

In addition, the paper on Intelligent roll-ups by Sunita Sarawagi is about roll-ups as opposed to drill down. So it assumes that the user is already at a detailed level of the table, has found an anomaly, and wants to `zoom out' to the highest level where the anomaly still exists. `Formalizing Complex Prior Information to Quantify Subjective Interestingness of Frequent Pattern Sets' uses a max entropy based approach, instead of maximizing total coverage of the table.

Based on Reviewer 1's suggestion, we will add a more detailed comparison between our contributions and existing work in Section 1 itself. Reviewers 1 and 2 also pointed out that some of the concepts and ideas introduced are simple. This is because we had moved a lot of the technical material, especially the sampling related work, to the technical report.

Reviewer 4 correctly points out that its the processing requirements of the priori algorithm than make the sampling procedure necessary, for the 2.5 million tuple dataset. The rule finding algorithm makes several passes over the dataset/sample, and would be very slow if it had to make many passes over a 2.5 million tuples. In this case, the sampling helps with speed, but can be done away with otherwise. On the other hand, users might want to explore even bigger datasets, containing billions of tuples, where the dataset doesn't fit in main memory at all, in which case the sampling scheme becomes even more essential.

### 2015-04-09 TableSummarization/Paper/KDDrebuttal.tex

\documentclass{article}
\date{\today}

\begin{document}

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle
To the editors,

We would like to thank the reviewers for their insightful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in the pattern mining area. Indeed, our paper considers a type of pattern mining, and should have cited the papers pointed out by the reviewers. However, there are significant differences with existing pattern mining work, which we believe make our paper interesting. We describe these differences below. We plan to significantly augment our related work section, describing the differences with the referenced papers and other pattern mining work.

There are three primary ways in which existing work on pattern mining differs from our work:
\begin{enumerate}
\item {\bf Interactiveness}: Smart drill-down allows the user to direct the data exploration according to his interests. This means that in each step, the number of rules displayed to the user should be small enough to be readable in a short amount of time, and the next set of rules to be displayed should depend on what part of the table the user expresses interest in. In addition, the response time of the system needs to be small ($< 10$ seconds) in order to prevent the user's flow of thought from being broken. In contrast, many of the mentioned related works (e.g. `The Chosen few', `Constraint based Pattern Mining') display {\em all} output patterns in one go, which would take a lot of processing time and potentially display unneeded information to the user. Some, such as `Krimp', `Summarizing Itemset Patterns: A Profile-Based Approach' display a smaller number of patterns, but are still not interactive. Note that our need for interactivity causes us to implement a smart memory manager that can use limited memory effectively while preparing for future drill down requests.

@@

\item {\bf Relational Data}: Smart drill-down is used for summarizing data from a relational table, as opposed to a set of transactions. Different columns in a table can be of differing importance to a user, and smart drill-down allows a user to focus on expanding certain columns, or to ignore certain columns. In a transaction based database, it is much harder to express extra interest in certain `types' of items.

\item {\bf Tunability}: An important attribute of our work is that we allow the user to specify the kind of rules he is interested in by specifying any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an {\em approximate optimality guarantee}. Thus we strike a balance between tunability and optimizability. This is in contrast to several of the related papers with a fully general scoring function (`Diverse subgroup set discovery', ), forcing the authors use an algorithm that is either heuristic with no optimality guarantees, or very time consuming. Some other papers (`MIME', `One click mining') are not tunable enough, and only provide a fixed set of interestingess parameters. 
\end{enumerate}

### 2015-04-10 TableSummarization/Paper/KDDrebuttal.tex

\begin{document}

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle
To the editors,

We would like to thank the reviewers for their insightful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in the pattern mining area. Indeed, our paper considers a type of pattern mining, and should have cited the papers pointed out by the reviewers. However, there are significant differences with existing pattern mining work, which we believe make our paper interesting. We describe these differences below. We plan to significantly augment our related work section, describing the differences with the referenced papers and other pattern mining work.

There are three primary ways in which existing work on pattern mining differs from our work:

Interactiveness: Smart drill-down allows the user to direct the data exploration according to his interests. This means that in each step, the number of rules displayed to the user should be small enough to be readable in a short amount of time, and the next set of rules to be displayed should depend on what part of the table the user expresses interest in. In addition, the response time of the system needs to be small (upto 10 seconds) in order to prevent the user's flow of thought from being broken. In contrast, many of the mentioned related works (e.g. `The Chosen few', `Constraint based Pattern Mining') display all output patterns in one go, which would take a lot of processing time and potentially display unneeded information to the user. Some, such as `Krimp', `Summarizing Itemset Patterns: A Profile-Based Approach' display a smaller number of patterns, but are still not interactive. Note that our need for interactivity causes us to implement a smart memory manager that can use limited memory effectively while preparing for future drill down requests.

Relational Data: Smart drill-down is used for summarizing data from a relational table, as opposed to a set of transactions. Different columns in a table can be of differing importance to a user, and smart drill-down allows a user to focus on expanding certain columns, or to ignore certain columns. In a transaction based database, it is much harder to express extra interest in certain `types' of items.

Tunability: An important attribute of our work is that we allow the user to specify the kind of rules he is interested in by specifying any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an `approximate optimality guarantee'. Thus we strike a balance between tunability and optimizability. This is in contrast to several of the related papers with a fully general scoring function (`Diverse subgroup set discovery', ), forcing the authors use an algorithm that is either heuristic with no optimality guarantees, or very time consuming. Some other papers (`MIME', `One click mining', `Finding Robust Itemsets Under Subsampling') are not tunable enough, and only provide a fixed set of interestingess parameters.

In addition, the paper on Intelligent roll-ups by Sunita Sarawagi is about roll-ups as opposed to drill down. So it assumes that the user is already at a detailed level of the table, has found an anomaly, and wants to `zoom out' to the highest level where the anomaly still exists. `Formalizing Complex Prior Information to Quantify Subjective Interestingness of Frequent Pattern Sets' uses a max entropy based approach, instead of maximizing total coverage of the table. Similarly, `A framework for mining interesting pattern sets' also uses a max entropy based approach and focuses on presenting `surprising' information to the user, based on the user's prior probability distribution.

Based on Reviewer 2's suggestion, we will add a more detailed comparison between our contributions and existing work in Section 1 itself. Reviewer 2 also pointed out that some of the concepts and ideas introduced are simple. This is because we had moved a lot of the technical material, especially the sampling related work, to the technical report.

Reviewer 4 mentions that our experiments don't show scalability, which is essential for KDD. The performance of our rule finding algorithm depends only on the sample size it runs on, so once our system creates a sample (in time linear in table size), it should have the same processing time for different sized datasets.

Reviewer 5 suggests we use a multivariate discretizer to preserve interactions, for continuous valued data. We thank the reviewer for this suggestion, and will incorporate this into our system.

Reviewer 6 correctly points out that it's the processing requirements of the apriori algorithm that make the sampling procedure necessary, for the 2.5 million tuple dataset. The rule finding algorithm makes several passes over the dataset/sample, and would be very slow if it had to make many passes over a 2.5 million tuples. In this case, the sampling helps with speed, but can be done away with otherwise. On the other hand, users might want to explore even bigger datasets, containing billions of tuples, where the dataset doesn't fit in main memory at all, in which case the sampling scheme becomes even more essential.

% address state of the art comment
% R6: number of attributes???

### 2015-04-10 TableSummarization/Paper/KDDrebuttal.tex

\documentclass{article}
\date{\today}

\begin{document}

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle

We would like to thank the reviewers for their insightful and incredibly useful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in pattern mining. Indeed, our paper considers a type of pattern mining, and should have cited the papers pointed out by the reviewers. However, there are significant differences with existing pattern mining work, which we believe make our paper interesting. We describe these differences below. We plan to significantly augment our related work section, describing the differences with the referenced papers and other pattern mining work.

@@

There are three primary ways in which existing work on pattern mining differs from our work:

1) Interactiveness: Smart drill-down allows the user to direct the data exploration according to his interests. This means that in each step, the number of rules displayed to the user should be small enough to be readable in a short amount of time, and the next set of rules to be displayed should depend on what part of the table the user expresses interest in. In addition, the response time of the system needs to be small (<10 seconds) in order to prevent the user's flow of thought from being broken. In contrast, many of the mentioned papers (e.g. `The Chosen few', `Constraint based Pattern Mining') display all output patterns in one go, which would take a lot of processing time and potentially display unneeded information to the user. Some, such as `Krimp', `Summarizing Itemset Patterns' display a smaller number of patterns, but are still not interactive. Note that our need for interactivity causes us to implement a smart memory manager that can use limited memory effectively while preparing for future requests.

2) Relational Data: Smart drill-down is used for summarizing data from a relational table, as opposed to a set of transactions. Different columns in a table can be of differing importance to a user, and smart drill-down allows a user to focus on expanding certain columns, while ignoring others. In a transaction based database, it is much harder to express extra interest in certain `types' of items.

3) Tunability: An important attribute of our work is that we allow the user to specify the kind of rules he/she is interested in by specifying any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an `approximate optimality guarantee'. Thus we strike a balance between tunability and optimizability. This is in contrast to related papers with a fully general scoring function (`Diverse subgroup set discovery'), forcing the use of an algorithm that is either heuristic with no optimality guarantees, or very time consuming. Some other papers (`MIME', `One click mining', `Finding Robust Itemsets Under Subsampling') are not tunable enough, and only provide a fixed set of interestingess parameters.

Further, the paper on Intelligent roll-ups by Sunita Sarawagi is about roll-ups as opposed to drill down. So it assumes that the user is already at a detailed level of the table, has found an anomaly, and wants to `zoom out' to the highest level where the anomaly still exists.
% `Formalizing Complex Prior Information to Quantify Subjective Interestingness of Frequent Pattern Sets' uses a max entropy based approach, instead of maximizing total coverage of the table. Similarly, `A framework for mining interesting pattern sets' also uses max entropy and focuses on presenting `surprising' information based on the user's prior probability distribution.

Based on Reviewer 2's suggestion, we will add a more detailed comparison between our contributions and existing work in Section 1 itself. Reviewer 2 also pointed out that we spent a little too much space on somewhat simple explanations;
this is again because we are outsiders to KDD and felt the need to explain things in detail. We'd be happy to move some of the more technical aspects and proofs from the technical report back into the paper once we shorten these explanations.

Reviewer 4 mentions that our experiments do not sufficiently demonstrate scalability. In fact, the performance of our rule finding algorithm depends only on the sample size it runs on, so once our system creates a sample (in time linear in table size), it should have the same processing time for different sized datasets.

Reviewer 5 suggests we use a multivariate discretizer to preserve interactions for continuous valued data. We thank the reviewer for this suggestion, and will incorporate this into our system.

Reviewer 6 correctly points out that it is the processing requirements of the apriori algorithm that make the sampling procedure necessary for the 2.5M tuple dataset. The rule finding algorithm makes several passes over the dataset, and would be very slow if it had to make many passes over so many tuples. Here, sampling helps with speed, but can be done away with otherwise. On the other hand, users might want to explore even bigger datasets, containing billions of tuples, where the dataset doesn't fit in main memory at all; here, sampling is not just a nice-to-have, it is a must-have.

### 2015-04-11 TableSummarization/Paper/KDDrebuttal.tex

\title{Smart Drill-Down (KDD Rebuttal)}
\author{Manas Joglekar, Hector Garcia-Molina, Aditya Parameswaran}
\maketitle

We would like to thank the reviewers for their insightful and incredibly useful comments. The primary comment made by every reviewer was that we had missed several papers related to our work. We are outsiders to the KDD community, and were not very familiar with previous work in pattern mining. Indeed, our paper considers a type of pattern mining, and should have cited the papers pointed out by the reviewers. However, there are significant differences with existing pattern mining work, which we believe make our paper interesting. We describe these differences below. We plan to significantly augment our related work section, describing the differences with the referenced papers and other pattern mining work.

There are three primary ways in which existing work on pattern mining differs from our work:

1) Interactiveness: Smart drill-down allows the user to direct the data exploration according to his interests. This means that in each step, the number of rules displayed to the user should be small enough to be readable in a short amount of time, and the next set of rules to be displayed should depend on what part of the table the user expresses interest in. In addition, the response time of the system needs to be small (<10 seconds) to prevent the user's flow of thought from being broken. In contrast, many of the mentioned papers (e.g. `The Chosen few', `Constraint based Pattern Mining') display all output patterns in one go, which would take a lot of processing time and potentially display unneeded information to the user. Some, such as `Krimp', `Summarizing Itemset Patterns' display a smaller number of patterns, but are still not interactive. Note that our need for interactivity causes us to implement a smart memory manager that can use limited memory effectively while preparing for future requests.

@@

2) Relational Data: Smart drill-down is used for summarizing data from a relational table, as opposed to a set of transactions. Different columns in a table can be of differing importance to a user, and smart drill-down allows a user to focus on expanding certain columns, while ignoring others. In a transaction based database, it is much harder to express extra interest in certain `types' of items.

3) Tunability: An important attribute of our work is that we allow the user to specify the kind of rules he/she is interested in by specifying any monotone weighting function. While this allows for a very wide variety of interestingness measures, the scoring function is restricted enough that it is submodular on the rule-set, allowing us to obtain an `approximate optimality guarantee'. Thus we strike a balance between tunability and optimizability. This is in contrast to related papers with a fully general scoring function (`Diverse subgroup set discovery'), forcing the use of an algorithm that is either heuristic with no optimality guarantees, or very time consuming. Some other papers (`MIME', `One click mining', `Finding Robust Itemsets Under Subsampling', `A framework for mining interesting pattern sets') are not tunable enough, and only provide a fixed set of interestingess parameters.

Further, the paper on `Intelligent roll-ups' is about roll-ups as opposed to drill down. It assumes that the user is already at a detailed level of the table, has found an anomaly, and wants to `zoom out' to the highest level where the anomaly still exists.

Based on Reviewer 2's suggestion, we will add a more detailed comparison between our contributions and existing work in Section 1 itself. Reviewer 2 also pointed out that we spent too much space on somewhat simple explanations;
this is again because we are outsiders to KDD and felt the need to explain things in detail. We'd be happy to move some of the more technical aspects and proofs from the technical report back to the paper once we shorten these explanations.

### 2015-06-23 TableSummarization/Paper/intro.tex
Added new related work

Our work on smart drill down is related
to table summarization and anomaly
detection~\cite{Sarawagi:2001:UMA:767141.767148,
Sarawagi00user-adaptiveexploration,
Sarawagi98discovery-drivenexploration,
DBLP:journals/pvldb/GebalyAGKS14}.
These papers mostly focus on
giving the most ``surprising'' information to the user, i.e., information
that would minimize the Kullback-Liebler(KL) divergence between the
resulting maximum entropy distribution and the actual value distribution. For instance, if a certain set of
values occur together in an unexpectedly small number of tuples, that
set of values may be displayed to the user. In contrast, our algorithm
focuses on rules with high counts, covering as
much of the table as possible.
Furthermore, our summarization is couched in
an interactive environment, where the analyst
directs the drill down and can tailor the optimization criteria.
Nevertheless, one can envision extending traditional
and smart drill down to provide an additional option of anomaly detection. We discuss related work in detail in  Section~\ref{sec:related}.

>>>>

Our work on smart drill down is related
to table summarization and anomaly
detection~\cite{Sarawagi:2001:UMA:767141.767148,
Sarawagi00user-adaptiveexploration,
Sarawagi98discovery-drivenexploration,
DBLP:journals/pvldb/GebalyAGKS14}.
These papers mostly focus on
giving the most ``surprising'' information to the user, i.e., information
that would minimize the Kullback-Liebler(KL) divergence between the
resulting maximum entropy distribution and the actual value distribution. For instance, if a certain set of
values occur together in an unexpectedly small number of tuples, that
set of values may be displayed to the user. In contrast, our algorithm
focuses on rules with high counts, covering as
much of the table as possible.
Furthermore, our summarization is couched in
an interactive environment, where the analyst
directs the drill down and can tailor the optimization criteria.
Nevertheless, one can envision extending traditional
and smart drill down to provide an additional option of anomaly detection. 
\mrjdel{We discuss related work in detail in  Section~\ref{sec:related}.}

\mrj{Our work is also related to pattern mining. Several of the pattern mining papers~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} focus on providing one shot summaries of data, and are not interactive. Moreover, to the best of our knowledge, all other pattern mining work is either not flexible enough~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117}, restricting the amount of tuning the user can perform, or so general~\cite{Leeuwen:2012:DSS:2347179.2347243} as to preclude efficient optimization. Our work also merges `interesting pattern mining' into the OLAP framework. We discuss related work in detail in Section~\ref{sec:related}.}

### 2015-06-23 TableSummarization/Paper/related.tex
Added new related work

Some related work~\cite{DBLP:journals/debu/GolabKS11, Golab:2008:GNT:1453856.1453900} focuses on finding minimum sized Tableaux that provide improved support and confidence for conditional functional dependencies. There has also been work~\cite{Bu:2005:MSH:1083592.1083644, Lakshmanan:2002:GMA:1287369.1287435, DBLP:conf/kdd/XiangJFD08, Geerts04tilingdatabases} on finding hyper-rectangle based covers for tables. In both these cases, the emphasis is on completely covering or 
summarizing the table, suffering from the same problems as traditional drill down in that the user may be presented with
too many results. The techniques in the former case may end up picking rare ``patterns'' if they have high confidence, and in the latter case do not scale well to a large number of attributes (in their case, $\geq 4$).

@@

% All the existing works solve a fixed optimization problem, whereas  we focus on finding an optimal summary for a flexible user-specified weighting function.

>>>>

Some related work~\cite{DBLP:journals/debu/GolabKS11, Golab:2008:GNT:1453856.1453900} focuses on finding minimum sized Tableaux that provide improved support and confidence for conditional functional dependencies. There has also been work~\cite{Bu:2005:MSH:1083592.1083644, Lakshmanan:2002:GMA:1287369.1287435, DBLP:conf:kdd:XiangJFD08, Geerts04tilingdatabases} on finding hyper-rectangle based covers for tables. In both these cases, the emphasis is on completely covering or 
summarizing the table, suffering from the same problems as traditional drill down in that the user may be presented with
too many results. The techniques in the former case may end up picking rare ``patterns'' if they have high confidence, and in the latter case do not scale well to a large number of attributes (in their case, $\geq 4$).

@@

\mrj{There has also been plenty of work on pattern mining. Several works~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} are non-interactive, and attempt to find a one shot summary of the table. This usually consumes a large amount of time processing the whole table, rather than allowing the user to slowly steer into portions of interest. In contrast, our work is interactive, and includes a smart memory manager that can use limited memory effectively while preparing for future requests.}

\mrj{Our Smart Drill-Down operator is tunable because of the flexible weighting function, but the monotonicity of the weighting function and the use of $MCount$, still make it possible for us to get an approximate optimality guarantee for the rules we display. In contrast, much of the existing pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117} is not not tunable enough, providing only a fixed set of interestingess parameters. On the other hand, reference~\cite{Leeuwen:2012:DSS:2347179.2347243} allows a fully general scoring function, necessitating the use of heuristics with no optimality guarantees, and very time consuming algorithms. 
A lot of pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Yan:2005:SIP:1081870.1081907,Vreeken:2011:KMI:1969593.1969615} also focuses on itemsets rather than Relational Data, which doesn't allow the user to express interest in certain `columns' over others.}
% All the existing works solve a fixed optimization problem, whereas  we focus on finding an optimal summary for a flexible user-specified weighting function.
